### 2016-07-25 paper/paper.tex
minor typos pass

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targeting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
DDoSed, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to how miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated as follows:
\begin{equation}
SHA256(txid || output\_script || N)
\end{equation}

@@

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS\@. Similarly, the client
commits to the output script of the claiming transaction to
prevent others from being able to swap it for their own, thereby ``stealing'' the
proof-of-DoS and collecting the reward themselves. These properties combined allow two
mutually-distrusting parties to directly and safely transact currency in
exchange for a specified-amount of work in a DoS attack.

@@

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their privileged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
and sufficiently difficult proof-of-work
would indicate to the bounty provider that the target is claiming its bounty.

@@

To evaluate the performance and effectiveness of DDoSCoin, we implement our
proof-of-DDoS function in 582 lines of C\@. Our mining code uses
libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
connections toward a specific target, crafting a
\texttt{client\_random} in the specified way and testing each response to see if it
satisfies a hard-coded proof-of-DDoS target difficulty.

@@

DDoSCoin uses a proof that the miner has connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much
bandwidth or resources are being spent by the victim. Although miners only
receive DDoSCoins in return for this effort, these can be traded in for other
currency via cryptocurrency exchanges. In addition, because DDoSCoin uses
transactions similar to Bitcoin, trust-less cross-chain transactions can allow
DDoSCoins to be traded for Bitcoins without requiring a trusted 3rd party
intermediary. Thus, even outlawing DDoSCoins from exchanges does not prevent a
black-market from getting around these sanctions.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowledge this work introduces an idea that could be used to incentivize 
malicious behavior, we have taken precautions to limit harm. First, in
demonstrating our proof-of-concept and evaluating our proof-of-DDoS code, we
have only ``attacked'' websites we have ownership and authority over.
Further, we are not publishing a working alt-coin that uses this proof-of-DDoS,
but rather a conceptual description of one.
We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long
TLS/SSL protocol versions stay in active use.

@@

The authors are grateful for the support and various discussions on DDoSCoin. We
thank David Adrian, Matt Bernhard, and Drew Springall for their discussions
concerning the feasibility of the proof-of-DDoS idea. We also thank the
anonymous reviewers for their helpful feedback.

>>>>

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targeting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
attacked, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to how miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated as follows:
\begin{equation}
SHA256(txid || output\_script || N)
\end{equation}

@@

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is committed to in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS\@. Similarly, the client
commits to the output script of the claiming transaction to
prevent others from being able to swap it for their own, thereby ``stealing'' the
proof-of-DoS and collecting the reward themselves. These properties combined allow two
mutually-distrusting parties to directly and safely transact currency in
exchange for a specified-amount of work in a DoS attack.

@@

Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. Any target specified by a PAY\_TO\_DDOS transaction
could use their privileged position to turn the proof-of-work into a computational challenge.
Since the challenge is no longer bound by the network, the target can claim the reward for
themselves. Quickly solved PAY\_TO\_DDOS transactions with no degradation of service
and sufficiently difficult proof-of-work
could indicate to the bounty provider that the target is claiming its bounty.

@@

To evaluate the performance and effectiveness of DDoSCoin, we implemented our
proof-of-DDoS function in 582 lines of C\@. Our mining code uses
libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
connections toward a specific target, crafting a
\texttt{client\_random} in the specified way and testing each response to see if it
satisfies a hard-coded proof-of-DDoS target difficulty.

@@

DDoSCoin uses a proof that the miner has connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much
bandwidth or resources are being spent by the victim. Although miners only
receive DDoSCoins in return for this effort, these can be traded in for other
currency via cryptocurrency exchanges. In addition, because DDoSCoin uses
transactions similar to Bitcoin, trust-less (atomic) cross-chain transactions can allow
DDoSCoins to be traded for Bitcoins without requiring a trusted 3rd party
intermediary. Thus, even outlawing DDoSCoins from exchanges does not prevent a
black-market from getting around these sanctions.

@@

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowledge this work introduces an idea that could be used to incentivize 
malicious behavior, we have taken precautions to limit harm. First, in
demonstrating our proof-of-concept and evaluating our proof-of-DDoS code, we
have only ``attacked'' websites we have ownership and authority over.
Furthermore, we are not publishing a working alt-coin that uses this proof-of-DDoS,
but rather a conceptual description of one.
We believe it is important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long
TLS/SSL protocol versions stay in active use.

@@

The authors are grateful for the support and various discussions from our
colleagues on DDoSCoin. In particular, the authors wish to thank David Adrian,
Matt Bernhard, and Drew Springall for their discussions concerning the
feasibility of the proof-of-DDoS idea. We also thank the anonymous reviewers
for their helpful feedback.
